State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-22 paper/chapters/4_classification.tex
paper: add general information about machine learning

\subsection{Machine Learning Algorithms}

Based on the preprocessed data a machine learning algorithm can be applied which aims to classify the polarity of the given input data. [...]
According to the paper by Qiang et al.\autocite{Ye20096527} the most important approaches in 
text mining and sentiment classification are Naive Bayes, Support Vector Machines and 
N-gram. Maximum Entropy Classification is also often mentioned by various papers regarding 
classification in sentiment analysis.

\subsubsection*{Na\"{\i}ve Bayes}

>>>>

\subsection{Methods}

For the actual classification process extent literature distinguishes two general types of techniques, namely \emph{machine learning} and \emph{semantic orientation} \cite{Ye20096527}. The machine learning approach is also referred to as \emph{supervised learning}, since corresponding techniques generally require supervised training phases. Accordingly, semantic orientation is also called \emph{unsupervised learning} because such a training phase is not necessary for the process to work. The most prominent machine learning methods comprise \emph{support vector machines} and the \emph{Na\"ive Bayes} classifier.

\subsubsection*{Na\"ive Bayes}
